---
title: "BIOS 6670-001 — HW #1"
author: 
  - Daniel Dulchevsky
  - Dr. Zhiying You
date: "CoSIBS Week 3"
output: 
  html_document:
    theme: readable
    code_folding: hide
    #toc: true
    #toc_float: true
---
```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
options(scipen=999)
```
<br/>

##### A. Generate data of two random samples of size $n=10$ from a normally distributed population with mean $\mu=10$ and $\sigma = 5$. The two samples can be considered an independent pair of samples.
```{r}
set.seed(1);

pop_mean = 10;
pop_sd = 5;
sample_size = 10;

sample_1 = rnorm(n=sample_size, mean=pop_mean, sd=pop_sd);
sample_2 = rnorm(n=sample_size, mean=pop_mean, sd=pop_sd);

cat("Sample 1: ", toString(round(sample_1, digits = 3)), "\n\n", 
    "Sample 1 Mean: ", mean(sample_1), "\n", 
    "Sample 1 SD: ", sd(sample_1), "\n\n", sep = "");

cat("Sample 2: ", toString(round(sample_2, digits = 3)), "\n\n", 
    "Sample 2 Mean: ", mean(sample_2), "\n", 
    "Sample 2 SD: ", sd(sample_2), "\n", sep = "");
```

<br/>
<br/>

##### B. Calculate $t$ statistics and the two-sided $p$-value just like those in comparing two sample means by using a $t$-test.
```{r}
t = (mean(sample_1)-mean(sample_2))/
    sqrt(((sd(sample_1))^2)/sample_size +((sd(sample_2))^2)/sample_size);

deg_free = (sample_size*2)-2;
p = pt(t, df=deg_free);

cat("t-score: ", t, "\n", "p-value: ", 2*p, sep = "");
```

<br/>
<br/>

##### C. Repeat steps A and B for 10,000 times. 
```{r class.source = 'fold-show'}

t_vector = vector("numeric", 10000L)
p_vector = vector("numeric", 10000L)
signif_p = 0

set.seed(1);

for (i in 1:10000)
{
  pop_mean = 10;
  pop_sd = 5;
  sample_size = 10;
  
  sample_1 = rnorm(n=sample_size, mean=pop_mean, sd=pop_sd);
  sample_2 = rnorm(n=sample_size, mean=pop_mean, sd=pop_sd);
  
  t = (mean(sample_1)-mean(sample_2))/
      sqrt(((sd(sample_1))^2)/sample_size + ((sd(sample_2))^2)/sample_size);

  deg_free = (sample_size*2)-2;
  
  p = pt(t, df=deg_free);
  
  if (p<=0.05)
  {
    signif_p = signif_p + 1;
  }
  
  t_vector[i] = t;
  p_vector[i] = p;
}
```

<br/>
<br/>

##### D. Calculate the proportion/percent of $p$-values that are NOT greater than 0.05.
```{R}
prop_signif_p = signif_p/10000;
percent_signif_p = prop_signif_p * 100;

cat("proportion: ", prop_signif_p, "\n", 
    "percent: ", percent_signif_p, sep = "")
```
This means that 5.29% of $p$-values (or 529 out of the total 10,000) are NOT greater than 0.05.

<br/>
<br/>

##### E. Discuss the null hypothesis, implication of $p$-values, and the proportion obtained.

Our null hypothesis is that there is no evidence of a difference between the two population means. Since the vast majority of $p$-values had a value *greater* than 0.05 (9,471 out of 10,000 to be exact), we fail to observe a statistically significant difference between the two sample means, and thus fail to reject the null hypothesis.

<br/>
$~$
<br/>

*End of Document*