---
title: "BIOS 6670-001 — HW #6"
author: 
  - Daniel Dulchevsky
  - Dr. Zhiying You
date: "CoSIBS Week 3"
output: 
  html_document:
    theme: readable
    code_folding: hide
    #toc: true
    #toc_float: true
---
```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
options(scipen=999)
```
<br/>

##### A. Obtain a random sample of size $n=30$ from a normally distributed population with mean $\mu = 10$ and standard deviation $\sigma=5$.
```{r}
set.seed(1);

pop_mean1 = 10;
pop_sd1 = 5;
sample_size1 = 30;

sample_1 = rnorm(n=sample_size1, mean=pop_mean1, sd=pop_sd1);

cat("Sample 1: ", toString(round(sample_1, digits = 3)), "\n\n", 
    "Sample 1 Mean: ", mean(sample_1), "\n", 
    "Sample 1 SD: ", sd(sample_1), "\n\n", sep = "");
```

<br/>
<br/>

##### B. Obtain a random sample of size $n=30$ from a normally distributed population with mean $\mu = 15$ and standard deviation $\sigma=5$.
```{r}
set.seed(1);

pop_mean2 = 15;
pop_sd2 = 5;
sample_size2 = 30;

sample_2 = rnorm(n=sample_size2, mean=pop_mean2, sd=pop_sd2);

cat("Sample 2: ", toString(round(sample_2, digits = 3)), "\n\n", 
    "Sample 2 Mean: ", mean(sample_2), "\n", 
    "Sample 2 SD: ", sd(sample_2), "\n\n", sep = "");
```

<br/>
<br/>

##### C. The two samples can be considered an independent pair of samples.

<br/>
<br/>

##### D. Perform a $t$-test to compare the two sample means with a two-sided significance level of 0.01.
```{R}
t = (mean(sample_1)-mean(sample_2))/
    sqrt(((sd(sample_1))^2)/sample_size1 +((sd(sample_2))^2)/sample_size2);

deg_free = (sample_size1*2)-2;
p = pt(t, df=deg_free);

cat("t-score: ", t, "\n", "p-value: ", 2*p, sep = "");
```
Since $p<$ 0.05, our results are statistically significant.

<br/>
<br/>

##### E. Repeat steps A to D 10,000 times.
```{R}
t_vector = vector("numeric", 10000L)
p_vector = vector("numeric", 10000L)
signif_p = 0

set.seed(1);

for (i in 1:10000)
{
  sample_1 = rnorm(n=sample_size1, mean=pop_mean1, sd=pop_sd1);
  sample_2 = rnorm(n=sample_size2, mean=pop_mean2, sd=pop_sd2);
  
  t = (mean(sample_1)-mean(sample_2))/
      sqrt(((sd(sample_1))^2)/sample_size1 + ((sd(sample_2))^2)/sample_size2);

  deg_free = (sample_size1*2)-2;
  
  p = pt(t, df=deg_free);
  
  if (p<=0.01)
  {
    signif_p = signif_p + 1;
  }
  
  t_vector[i] = t;
  p_vector[i] = p;
}
```

<br/>
<br/>

##### F. Calculate the proportion/percent of conclusions that DO NOT reject the null.
```{R}
prop_insignif_p = 1-(signif_p/10000);
percent_insignif_p = prop_insignif_p * 100;

cat("proportion: ", prop_insignif_p, "\n", 
    "percent: ", percent_insignif_p, sep = "")
```
This means that only 7.04% of the $p$-values (or 704 out of the total 10,000) DO NOT reject the null hypothesis (i.e., 92.96% of the $p$-values DO reject the null hypothesis).

<br/>
$~$
<br/>

*End of Document*