---
title: "BIOS 6670-001 — HW #8"
author: 
  - Daniel Dulchevsky
  - Dr. Zhiying You
date: "CoSIBS Week 3"
output: 
  html_document:
    theme: readable
    code_folding: hide
    #toc: true
    #toc_float: true
---
```{r include=FALSE}
knitr::opts_chunk$set(comment = NA)
options(scipen=999)
```
<br/>

##### Select three pairs of sample means of t-tests with and without rejection of the null, respectively, from Homework #3.

```{r}
sample_size_a = 10;
sample_size_b = 10;

reject_null_2a = 0;
reject_null_2b = 0;
reject_null_3a = 0;
reject_null_3b = 0;

dont_reject_null_2a = 0;
dont_reject_null_2b = 0;
dont_reject_null_3a = 0;
dont_reject_null_3b = 0;

set.seed(1);

for (i in 1:10000)
{
  sample_a = rnorm(n=sample_size_a, mean=10, sd=5);
  sample_b = rnorm(n=sample_size_b, mean=15, sd=5);
  
  t = (mean(sample_a)-mean(sample_b))/
      sqrt(((sd(sample_a))^2)/sample_size_a + ((sd(sample_b))^2)/sample_size_b);

  deg_free = (sample_size_a*2)-2;
  
  p = pt(t, df=deg_free);
  
  if (2*p<=0.05)
  {
    reject_null_1a = reject_null_2a;
    reject_null_1b = reject_null_2b;
    
    reject_null_2a = reject_null_3a;
    reject_null_2b = reject_null_3b;
    
    reject_null_3a = sample_a;
    reject_null_3b = sample_b;
    
  }
  
  else
  {
    dont_reject_null_1a = dont_reject_null_2a;
    dont_reject_null_1b = dont_reject_null_2b;
    
    dont_reject_null_2a = dont_reject_null_3a;
    dont_reject_null_2b = dont_reject_null_3b;
    
    dont_reject_null_3a = sample_a;
    dont_reject_null_3b = sample_b;
  }
  
}

cat("Pairs of Samples that DO reject the null: ", "\n\n\t", 
    
    "Pair 1: ", toString(round(reject_null_1a, digits = 3)), "\n\t\t\t", 
                toString(round(reject_null_1b, digits = 3)), "\n\n\t",
    
    "Pair 2: ", toString(round(reject_null_2a, digits = 3)), "\n\t\t\t", 
                toString(round(reject_null_2b, digits = 3)), "\n\n\t",
    
    "Pair 3: ", toString(round(reject_null_3a, digits = 3)), "\n\t\t\t", 
                toString(round(reject_null_3b, digits = 3)), "\n\n\n", 
                sep = "");

cat("Pairs of Samples that DO NOT reject the null: ", "\n\n\t", 
    
    "Pair 1: ", toString(round(dont_reject_null_1a, digits = 3)), "\n\t\t\t", 
                toString(round(dont_reject_null_1b, digits = 3)), "\n\n\t",
    
    "Pair 2: ", toString(round(dont_reject_null_2a, digits = 3)), "\n\t\t\t", 
                toString(round(dont_reject_null_2b, digits = 3)), "\n\n\t",
    
    "Pair 3: ", toString(round(dont_reject_null_3a, digits = 3)), "\n\t\t\t", 
                toString(round(dont_reject_null_3b, digits = 3)), "\n", 
                sep = "");
```
<br/>

##### Calculate the 95% confidence interval for the difference of the two population means.
```{r class.source = 'fold-show'}
t.test(sample_a, sample_b, var=T);
```
According to the output of the above `t.test()` function, our 95% confidence interval for the difference of the two population means is approximately (-12.8, -3.3).

<br/>

##### Discuss the relationship between test and confidence interval.
The t-test and confidence interval are related in that a t-test would reject the null hypothesis if and only if the confidence interval does not contain 0. Likewise, a t-test fails to reject the null hypothesis if and only if the confidence interval does contain 0.

<br/>
$~$
<br/>

*End of Document*